---
title: "CARPS Reproducibility Report"
output:
  html_document:
    toc: true
    toc_float: true
---

#### Article ID: [CARPS_4-1-2015_PS]
#### Pilot 1: [Sean Zion]
#### Co-pilot: [Mufan Luo]
#### Start date: [11/5/2017]
#### End date: [11/6/2017]   

-------

#### Methods summary: 
[Write a brief summary of the methods underlying the target outcomes written in your own words]

------

#### Target outcomes: 
[Insert the target outcomes identified in targetOutcomes.md]  

------



```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo=TRUE, warning=FALSE, message=FALSE)
```

## Step 1: Load packages


```{r}
library(tidyverse) # for data munging
library(knitr) # for kable table formating
library(haven) # import and export 'SPSS', 'Stata' and 'SAS' Files
library(readxl) # import excel files
library(CARPSreports) # custom report functions
library(ggplot2)
library(psych)
library(plyr)
library(corrplot)
library(car)
library(ez)
```

## Step 2: Load data

```{r}
faces <- read.csv("/Users/seanzion/Documents/GitHub/CARPS_4-1-2015_PS/data/Experiment _1_Rps _v2.csv")
```

## Step 3: Tidy data

```{r}
faces$id <- c(1:48) #adding a new column for subject ID

tidyfaces <- faces %>%
  gather(key="DFT_Rating", value, 3:35) %>%
  separate(DFT_Rating, c("dft", "value_trial"), sep="T_") %>%
  subset(select = -dft) %>%
  separate(value_trial, c("dft_value", "trial_num"), sep="_") %>% 
  spread(trial_num, value)

```

## Step 4: Run analysis

### Pre-processing

```{r}
colnames(tidyfaces) <- c("age", "trust_attract", "id", "dft_value", "trial_1", "trial_2", "trial_3") #renaming the columns 

avg_value <-rowMeans(tidyfaces[,5:7]) #Calculating the avg value for each participant across the three tirals
tidyfaces$avg_value <- avg_value #adding this column into the dataframe

tidyfaces$dft_value <- as.numeric(tidyfaces$dft_value)
tidyfaces$trust_attract <- as.factor(tidyfaces$trust_attract)
```

### Descriptive statistics

```{r}
#Mean and SD for ratings across judement type (trustworthy / attractiveness):

tidyfaces %>%
  filter(trust_attract==1) %>%
  summarise(mean = mean(avg_value), 
            sd = sd(avg_value))

tidyfaces %>%
  filter(trust_attract==0) %>%
  summarise(mean = mean(avg_value), 
            sd = sd(avg_value))

attract_mean = c()
attract_sd = c()
trust_mean = c()
trust_sd = c()

for (i in 0:10){
  a = tidyfaces %>%
  filter(trust_attract==0 & dft_value == 10*i) %>%
  summarise(mean = mean(avg_value), 
            sd = sd(avg_value))
  attract_mean = c(attract_mean, a$mean)
  attract_sd = c(attract_sd, a$sd)

  
  t = tidyfaces %>%
  filter(trust_attract==1 & dft_value == 10*i) %>%
  summarise(mean = mean(avg_value), 
            sd = sd(avg_value))
  trust_mean = c(trust_mean, t$mean)
  trust_sd = c(trust_sd, t$sd)
}

df = data.frame("dft_value"=seq(0,100,10))
df = mutate(df, "trust_mean" = trust_mean
            , "trust_sd" = trust_sd
            , "attract_mean" = attract_mean
            , "attract_sd" = attract_sd)

print(df)

```

We are really interested in the mean(SD) judgement for attractiveness and trustworthiness for all participants for each value of DFT. It was simplier to find this using a for loop to calculate each of the 20 mean values and enter them into a dataframe.

### Inferential statistics

```{r, model 1}

#Model 1 - Repeated Measures ANOVA 
tidyfaces$trust_attract = as.factor(tidyfaces$trust_attract)
tidyfaces$dft_value = as.factor(tidyfaces$dft_value)
tidyfaces$id = as.factor(tidyfaces$id)
model1 <- with(tidyfaces, aov(avg_value ~ dft_value * trust_attract + Error(id / dft_value)))
summary(model1)
```

Our goal was to reproduce the analysis of the authors in experiemnt one. we conducted a by-participant repeated measures analysis of variance using the value of DFT as a repeated measure and judgment type (either trustworthiness or attractiveness) as a between-subjects factor.

The main effect of DFT was significant, F(10, 46) = 10.50, p < .001. There was also a significant interaction between DFT and Judgement Type  interaction, F(10, 460) = 43.75, p < .001.

ηp2 could not be caluculated with this model, but we will check this output and calculate ηp2 below. 

```{r, mod 2}
#Model 2 - Repeated Measures ANOVA
tidyfaces$trust_attract <- as.factor(tidyfaces$trust_attract)
tidyfaces$dft_value <- as.factor(tidyfaces$dft_value)
tidyfaces$id <- as.factor(tidyfaces$id)
model2 <- ezANOVA(data = tidyfaces, dv = .(avg_value), wid = .(id), within = .(dft_value), between = .(trust_attract), detailed = TRUE, return_aov=T)

model2$ANOVA
print(model2)
```

Because we found differnt outcomes above and we could not obtain all the values reported by the authors, here we try a slightly differnt model using a different R package.

The main effect of DFT was significant, F(10, 46) = 10.49, p < .001, ηp2 = 0.082. There was also a significant interaction between DFT and Judgement Type  interaction, F(10, 460) = 43.75, p < .001, ηp2 = 0.27.


```{r, Fig 2 Rep}
#Figure 2 Replication
pd <- position_dodge(0.1)
ggplot() + 
  geom_line(data = df, aes(x = dft_value, y = attract_mean), color = "green") + 
    geom_errorbar(aes(x = df$dft_value, ymin = attract_mean - attract_sd/sqrt(528), ymax = attract_mean + attract_sd/sqrt(528)), width=.1, position = pd)  + geom_line(data = df, aes(x = dft_value, y = trust_mean), color = "blue") +
  geom_errorbar(aes(x = df$dft_value, ymin = trust_mean - trust_sd/sqrt(528), ymax = trust_mean + trust_sd/sqrt(528)), width=.1,
position = pd)  +  xlab('DFT Value') + ylab('Mean Judgment') + ylim(0, 10) + scale_x_continuous(breaks=seq(0,100,10))

```

Figure 2: Mean trustworthiness and attractiveness judgments as a function of DFT. Error bars represent within-subjects standard errors.

```{r}

#ANOVA Output - Main Effect of DFT
compareValues(reportedValue = 4.05, obtainedValue = 10.50)


#ANOVA Output - Interaction Effect of DFT with Judgment Type
compareValues(reportedValue = 5.95, obtainedValue = 43.75)


#ANOVA Output - F Test Degrees of Freedom 
compareValues(reportedValue = 37, obtainedValue = 46)

```

## Step 5: Conclusion

```{r}

carpsReport(Report_Type = "pilot", 
             Article_ID = "CARPS_4-1-2015_PS", 
             Insufficient_Information_Errors = 0, 
             Decision_Errors = 0, 
             Major_Numerical_Errors = 3, 
             Time_to_Complete = 500, 
             Author_Assistance = TRUE)
```

In conclusion, we attempted to replicate a main finding from the Sofer et al., paper. The authors conducted a by-participant repeated measures analysis of variance (ANOVA) with DFT as a repeated measure and judgment type (trustworthiness vs. attractiveness) as a between-subjects factor. They report a significant main effect of DFT ( F(10, 37) = 4.05, p < .001, ηp2 = .52). The authors also found a significant interaction, F(10, 37) = 5.95, p < 0.001, ηp2 = 0.62

Our attempt to calculate these same findings failed. We believe this could be due to confusion over the number of subjects included. As reported above, it looks as though the authors only inlcuded 38 of the 48 subjects, indicated by a DF=37, or this was a typo in the manuscript. If certain participants were excluded from the analysis, it was not indicated other than the above DF error.

We found nearly identical values in two different ANOVA models, both of which differed from the authors reported findings.

We were generally able to replicate the figure depicting mean trustworthiness and attractiveness judgments as a function of distance of the face from the typical face (DFT).


```{r session_info, include=TRUE, echo=TRUE, results='markup'}
devtools::session_info()
```
